---
title: "Plot and Descriptive Stats for Covid Project"
output: 
  rmarkdown::github_document:
    toc: true
    #toc_float: true
    toc_depth: 4
---

This is an R Markdown file to reproduce figures in manuscript 'Overestimating the intensity of negative emotion in autobiographical memory: evidence from the 9/11 attack and Covid-19 pandemic'

For regression analysis, please see MCMC_analyses_notebook.Rmd

Besides providing the data files needed to run the analysis, we have also provided a saved rds file storing all the MCMC objects. You could download it from OSF [OSF link] and place it in the data folder

For any question, contact Haoxue (haoxue_fan@g.harvard.edu) or Johnny (jcastillo@g.harvard.edu)

```{r load dependency and datafile, include=FALSE}
source('utils.R')
# here we need to use one of the regression object to generate predictions. 
# if you wish to load in the saved RData file, uncomment the line below
load(file = '../data/BayesRegObj.RData')

# read in data
covid_wide <-  read.csv('../data/Complete_test_Dev_Exp_Only_Data_Manipulation.csv') #each row is one observation, T1 and T2 separated by prefix in the colnmae
nine11_wide_avg <- read.csv('../data/df.emo.wide.avg_Only_Data_Manipulation.csv') #each row is one observation at one time point, stress_memory is avg across emotions
nine11_wide <- read.csv('../data/df.emo.wide_Only_Data_Manipulation.csv') #each row is one observation at one time point, stress_memory is specific to one emotion
nine11_long_avg <- read.csv('../data/df.emo.long.avg_Only_Data_Manipulation.csv') #each row is one observation at one time point, stress_memory is avg across emotions

#  filter time2 data frome 911 to do shared analysis 
nine11_long_avg_T2 <- nine11_long_avg %>% filter(time==2)
nine11_wide_T2 <- nine11_wide %>% dplyr::select(!ends_with('3') & !ends_with('4'))
```

# Supplementary Fig1 : Time interval between the initial and the follow-up questionnaire filled out date for the Covid-19 dataset

```{r delta time}
# delta time
covid_wide$Dat_Delta <- as.Date(covid_wide$T2_StartDate) - as.Date(covid_wide$T2_Dat)
mean(covid_wide$Dat_Delta)
sqrt(var(covid_wide$Dat_Delta))

covid_wide %>% ggplot(aes(x=as.double(Dat_Delta))) +
   geom_histogram(color='black') +
   xlab('T2-T1 (days)') +
  emomem_theme

ggsave('../Output/fig/pdf/Supp_delta_date.pdf', height=6, width=8)
ggsave('../Output/fig/png/Supp_delta_date.png', height=6, width=8)
```

# Supplementary Table 9 for Covid related stressors
```{r}
T1_covid_header <- read.csv('../data-raw/COVIDdata_vertical_new_q.csv')
T1_covid_item <- T1_covid_header %>% filter(str_detect(Header, 'lifechanges'))
T1_covid_item %>% mutate(Item = str_replace(Item, 'How much stress are you experiencing right now as a result of...', '')) %>% dplyr::select(Item) %>% rename(`How much stress are you experiencing right now as a result of...`=Item) %>% 
  as.data.frame %>% write.csv('../Output/csv/Supp_T1_covid_item.csv')
```

# Supplementary Table 10. Loading Matrix for PCA
```{r PCA Loading Matrix}

df.prev_pca <- covid_wide %>% dplyr::select(T2_prolific_mturk_ID, starts_with('T1_PSS') & !contains('total'), starts_with('T1_DASS') & !contains('total')) %>% na.omit 
prev_pca <- df.prev_pca %>% dplyr::select(-T2_prolific_mturk_ID) %>% 
  prcomp(center=TRUE, scale. =TRUE)

df.curr_pca <- covid_wide %>% dplyr::select(T2_prolific_mturk_ID, 
                                   starts_with('T2_PSS') & !contains('total'), 
                                   starts_with('T2_DASS') & !contains('total')) %>% 
  na.omit %>% 
  mutate(T2_PSS_4=4-T2_PSS_4, T2_PSS_5=4-T2_PSS_5, T2_PSS_7=4-T2_PSS_7, T2_PSS_8=4-T2_PSS_8) %>% 
  set_colnames(colnames(df.prev_pca))

df.prev_pca$prev_pca_score <- (prev_pca$x[,1]) * (-1)
df.curr_pca$curr_pca_score <- ((prev_pca %>% predict(df.curr_pca %>% dplyr::select(-T2_prolific_mturk_ID)))[,1]) * (-1)

# loading matrix
loading.prev_pca <- data.frame(Loading = prev_pca$rotation[,1]) %>% rownames_to_column(var='T1_Scale_Item') %>% 
  mutate(Scale = str_extract(T1_Scale_Item, 'PSS|DASS'), Index = str_extract(T1_Scale_Item, '(?<=_)[0-9]+'))
loading_header.prev_pca <- T1_covid_header %>% filter(str_detect(Header,'PSS_') | str_detect(Header, 'DASS21_')) %>% 
  mutate(Scale = str_extract(Header, 'PSS|DASS'), Index = str_extract(Header, '(?<=_)[0-9]+')) 
loading.prev_pca %>% merge(loading_header.prev_pca, by = c('Scale','Index')) %>% dplyr::select(Scale, Item, Loading) %>% 
  mutate(Loading = round(Loading, 3)) %>% 
  write.csv('../Output/csv/Supp_PCA_loading.csv')

```
# Supplementary Table 11 Correlation between subjective well-being score and psychological scales
```{r correlate with subscale}
covid_wide <- covid_wide %>% 
  mutate(T1_PSS_total = rowSums(covid_wide %>% dplyr::select(T1_PSS_1:T1_PSS_10)),
         T2_PSS_total = T2_PSS_1 + T2_PSS_2 + T2_PSS_3 + 4 - T2_PSS_4 + 4 - T2_PSS_5 + T2_PSS_6 + 4 - T2_PSS_7 + 4 - T2_PSS_8 + T2_PSS_9 + T2_PSS_10,
         T1_DASS_total_S = T1_DASS_1 + T1_DASS_6 + T1_DASS_8 + T1_DASS_11 + T1_DASS_12 + T1_DASS_14 + T1_DASS_18,
         T1_DASS_total_A = T1_DASS_2 + T1_DASS_4 + T1_DASS_7 + T1_DASS_9 + T1_DASS_15 + T1_DASS_19 + T1_DASS_20,
         T1_DASS_total_D = T1_DASS21_3_Depression + T1_DASS_5 + T1_DASS_13 +T1_DASS_16 + T1_DASS_17 + T1_DASS_21,
         T2_DASS_total_S = T2_DASS_1 + T2_DASS_6 + T2_DASS_8 + T2_DASS_11 + T2_DASS_12 + T2_DASS_14 + T2_DASS_18,
T2_DASS_total_A = T2_DASS_2 + T2_DASS_4 + T2_DASS_7 + T2_DASS_9 + T2_DASS_15 + T2_DASS_19 + T2_DASS_20,
T2_DASS_total_D = T2_DASS_3 + T2_DASS_5 + T2_DASS_13 +T2_DASS_16 + T2_DASS_17 + T2_DASS_21,
neg_PCA_T1 = -PCA_T1,
neg_PCA_T2 = -PCA_T2
           )

r_pca <- covid_wide %>% dplyr::select(neg_PCA_T1, neg_PCA_T2, T1_PSS_total, T1_DASS_total_A, T1_DASS_total_D, T1_DASS_total_S, 
                      T2_PSS_total, T2_DASS_total_A, T2_DASS_total_D, T2_DASS_total_S) %>% as.matrix() %>% 
  rcorr()
r_pca_rowname <- c('T1 Subjective Well-being', 'T2 Subjective Well-being', 'T1 PSS', 'T1 DASS Anxiety', 'T1 DASS Depression', 'T1 DASS Stress','T2 PSS', 'T2 DASS Anxiety', 'T2 DASS Depression', 'T2 DASS Stress' )
r_pca$r[,1:2] %>% round(3) %>% 
  set_rownames(r_pca_rowname) %>% 
  set_colnames(r_pca_rowname[1:2]) %>% 
  write.csv('../Output/csv/r_pca.csv')
```


# Figure 1
```{r Figure 1}

# Fig 1A
covid_long_type <- covid_wide %>% mutate(BCovid_Exp1 = beta_squeeze((Covid_Exp1-1)/4),
                                         BCovid_Exp2 = beta_squeeze((Covid_Exp2-1)/4),
                                         BCovid_Rem = beta_squeeze(Covid_Rem-1)/4) %>% 
  pivot_longer(cols = c('BCovid_Exp1','BCovid_Exp2','BCovid_Rem'),
               names_to = 'MemType', values_to = 'BStress') %>% 
  mutate(MemType = relevel(factor(MemType), ref='BCovid_Exp1')) %>% 
  filter(!is.na(BStress))

covid_long_type_plot <- covid_wide %>% mutate(BCovid_Exp1 = beta_squeeze((Covid_Exp1-1)/4),
                                         BCovid_Exp2 = beta_squeeze((Covid_Exp2-1)/4),
                                         BCovid_Rem = beta_squeeze(Covid_Rem-1)/4) %>% 
  pivot_longer(cols = c('Covid_Exp1','Covid_Exp2','Covid_Rem'),
               names_to = 'MemType', values_to = 'Stress') %>% 
  mutate(MemType = factor(MemType, levels = c('Covid_Exp1','Covid_Exp2','Covid_Rem'),
                          labels = c('Previous ', 'Current ', 'Remembered'))) %>% 
  filter(!is.na(Stress)) 
  

fig1A <- covid_long_type_plot %>% ggplot(aes(x = MemType, y = Stress)) + 
  stat_summary(size=1.7) 

fig1A + emomem_theme + 
  ylab('Average Stress') +
  xlab('') 
ggsave('../Output/fig/pdf/fig_stress_compare.pdf',height=6,width=7)
ggsave('../Output/fig/png/fig_stress_compare.png',height=6,width=7)
  
 # Fig 1B
nine11_long_type <- nine11_long_avg_T2 %>% 
  mutate(B911_Exp1 = beta_squeeze((prev_experience-1)/4),
         B911_Exp2 = beta_squeeze((curr_experience-1)/4),
         B911_Rem = beta_squeeze((stress_memory-1)/4)) %>% 
  pivot_longer(cols = c('B911_Exp1', 'B911_Exp2','B911_Rem'),
               names_to = 'MemType', values_to = 'BNegEmo') %>% 
  mutate(MemType = relevel(factor(MemType), ref='B911_Exp1')) %>% 
  filter(!is.na(BNegEmo))

nine11_long_type_plot <- nine11_long_avg_T2 %>% 
  mutate(B911_Exp1 = beta_squeeze((prev_experience-1)/4),
         B911_Exp2 = beta_squeeze((curr_experience-1)/4),
         B911_Rem = beta_squeeze((stress_memory-1)/4)) %>% 
  pivot_longer(cols = c('prev_experience', 'curr_experience','stress_memory'),
               names_to = 'MemType', values_to = 'NegEmo') %>% 
  mutate(MemType = factor(MemType, levels = c('prev_experience','curr_experience','stress_memory'),
                          labels = c('Previous ', 'Current ', 'Remembered'))) %>% 
  filter(!is.na(NegEmo))

fig1B <- nine11_long_type_plot %>% ggplot(aes(x = MemType, y = NegEmo)) + 
  stat_summary(size=1.2)
fig1B + emomem_theme + 
  ylab('Average Negative Emotion Intensity') +
  xlab('') 
ggsave('../Output/fig/pdf/fig_negemo_compare.pdf',height=6,width=7)
ggsave('../Output/fig/png/fig_negemo_compare.png',height=6,width=7)
  

# Fig 1C
# not quite sure how to deal with this...
```



```{r Fig 2}
# Fig 2A

# because we want y to be on its original scale, we need to extract the data and can not use plot_model_IVs_stan wrapper

covid_BRem <- covid_wide %>% mutate(BCovid_Rem = beta_squeeze((Covid_Rem-1)/4)) %>% 
  filter(!is.na(BCovid_Rem)) %>% filter(!is.na(Covid_Exp1)) %>% filter(!is.na(Covid_Exp2))
if (!exists("Rem_covid_MCMC_weighted")) {
Rem_covid_MCMC_weighted <- stan_glm(BCovid_Rem ~ Covid_Exp1 + Covid_Exp2,
                                  family = mgcv::betar, iter= niters, 
                           weights = num_weights_3var, seed = seed_no, data = covid_BRem)
}

df_Rem_covid_MCMC_weighted <- Rem_covid_MCMC_weighted %>% plot_model_IVs_stan(variable_array = c('Covid_Exp1','Covid_Exp2'),
                                              x_range = seq(1,5,by=0.2), return_df = TRUE) %>% as.data.frame
df_Rem_covid_MCMC_weighted <- df_Rem_covid_MCMC_weighted %>% mutate(
  across(!starts_with("x"), 
         function(x){return(reverse_beta_squeeze(x, n= length(covid_BRem$BCovid_Rem), likert_min_max = c(1,5)))},
         .names = "{.col}_original"))
 

p_Rem_covid_MCMC_weighted <- df_Rem_covid_MCMC_weighted %>% ggplot(aes_string(x = "x", y = "predicted_original", group = "x_name", color = "x_name")) +
    geom_line() +
    geom_ribbon(aes_string(ymin = "ymin_original",
                           ymax = "ymax_original" , fill = "x_name"), alpha = 0.3, color=NA,
                show.legend = FALSE)
  

p_Rem_covid_MCMC_weighted + 
  ylab('Remembered Negative Feelings') +
  ylim(1,5)+
  xlab('Experienced Negative Feelings') +
  scale_color_manual(labels = c('Previous','Current (after 1 year)'), values = palette2var)+
  scale_fill_manual(values = palette2var)+
  labs(colour='') + 
  emomem_theme

ggsave('../Output/fig/pdf/fig_recency_covid_new.pdf',height=6,width=6)
ggsave('../Output/fig/png/fig_recency_covid_new.png',height=6,width=6)

# Fig 2C
nine11_BRem_T2 <- nine11_long_avg_T2 %>% mutate(B911_Rem = beta_squeeze((stress_memory-1)/4)) %>% 
  filter(!is.na(B911_Rem)) %>% filter(!is.na(prev_experience)) %>% filter(!is.na(curr_experience))
if (!exists("Rem_911_MCMC_T2_weighted")) {
Rem_911_MCMC_T2_weighted <- stan_glm(B911_Rem ~ prev_experience + curr_experience,
                                    family = mgcv::betar, iter= niters, seed=seed_no,
                                    weights = num_weights_updated, data = nine11_BRem_T2)
}

df_Rem_911_MCMC_T2_weighted <- Rem_911_MCMC_T2_weighted %>% plot_model_IVs_stan(variable_array = c('prev_experience','curr_experience'),
                                              x_range = seq(1,5,by=0.2), return_df = TRUE) %>% as.data.frame

df_Rem_911_MCMC_T2_weighted <- df_Rem_911_MCMC_T2_weighted %>% mutate(
across(!starts_with("x"), 
         function(x){return(reverse_beta_squeeze(x, n= length(nine11_BRem_T2$B911_Rem), likert_min_max = c(1,5)))},
         .names = "{.col}_original"))
 
p_Rem_911_MCMC_T2_weighted <- df_Rem_911_MCMC_T2_weighted %>% ggplot(aes_string(x = "x", y = "predicted_original", group = "x_name", color = "x_name")) +
    geom_line() +
    geom_ribbon(aes_string(ymin = "ymin_original",
                           ymax = "ymax_original" , fill = "x_name"), alpha = 0.3, color=NA,
                show.legend = FALSE)

p_Rem_911_MCMC_T2_weighted + 
  ylab('Remembered Negative Feelings') +
  ylim(1,5)+
  xlab('Experienced Negative Feelings') +
  scale_color_manual(labels = c('Previous','Current (after 1 year)'), values = palette2var)+
  scale_fill_manual(values = palette2var)+
  labs(colour='') +
  emomem_theme
ggsave('../Output/fig/pdf/fig_recency_911_T2_new.pdf',height=6,width=6)
ggsave('../Output/fig/png/fig_recency_911_T2_new.png',height=6,width=6)

```

```{r mcmc interval}
# Fig 2B and 2D
p_coef_covid_weighted <- mcmc_intervals(as.array(Rem_covid_MCMC_weighted), pars = c('Covid_Exp1','Covid_Exp2'),
                                        prob_outer = 0.95)

p_coef_covid_weighted_area <- mcmc_areas(as.array(Rem_covid_MCMC_weighted), pars = c('Covid_Exp1','Covid_Exp2'),
                                        prob = 0.95)


p_coef_911_weighted_T2 <- mcmc_intervals(as.array(Rem_911_MCMC_T2_weighted), pars = c('prev_experience','curr_experience'), prob_outer = 0.95)

p_coef_911_weighted_T2_area <- mcmc_areas(as.array(Rem_911_MCMC_T2_weighted), pars = c('prev_experience','curr_experience'), prob = 0.95)

p_coef_covid_weighted_area + emomem_theme + 
  xlab('Coefficient Estimate') +
  scale_y_discrete(breaks = c('Covid_Exp1','Covid_Exp2'),
                   labels = c('Previous','Current\n(after 1 year)'))
ggsave('../Output/fig/pdf/fig_recency_coef_covid_area.pdf',height=6,width=6)
ggsave('../Output/fig/png/fig_recency_coef_covid_area.png',height=6,width=6)
  
p_coef_911_weighted_T2_area + emomem_theme +
  xlab('Coefficient Estimate') +
  scale_y_discrete(breaks = c('prev_experience','curr_experience'),
                   labels = c('Previous','Current\n(after 1 year)'))
ggsave('../Output/fig/pdf/fig_recency_coef_911_area.pdf',height=6,width=6)
ggsave('../Output/fig/png/fig_recency_coef_911_area.png',height=6,width=6)

```

```{r}

covid_long_pca <- covid_wide %>% mutate(neg_PCA_T1 = -PCA_T1, neg_PCA_T2 = -PCA_T2) %>%
  filter(!is.na(neg_PCA_T1) & !is.na(neg_PCA_T2)) %>% pivot_longer(cols = c('neg_PCA_T1','neg_PCA_T2'),
                            names_to = 'time',
                            values_to = 'Subjective_Well_being') %>% 
  dplyr::select(Subject, time, Subjective_Well_being) %>% 
  mutate(time = factor(time, levels = c('neg_PCA_T1','neg_PCA_T2'),
                       labels = c('Previous','Current (after 1 year)')))

p_covid_long_pca <- covid_long_pca %>% ggplot(aes(x=time, y=Subjective_Well_being)) + 
  stat_summary() 
p_covid_long_pca + emomem_theme + 
  xlab('Time') + ylab('Subjective Well-being')

ggsave('../Output/fig/pdf/supp_pca.pdf',height=6,width=7)
ggsave('../Output/fig/png/supp_pca.png',height=6,width=7)

```



```{r well-being}
covid_percent <- covid_wide %>% 
  mutate(BCovid_Dev = beta_squeeze((Covid_Dev+4)/8)) %>% 
  mutate(Percent = Covid_Dev / twovar_Covid_Exp1) %>% filter(!is.na(Percent)) %>% 
  filter(!is.na(BCovid_Dev)) %>% filter(!is.na(emo_well_being_delta))

if (!exists("covid_delta_EmoWell_MCMC")) {
covid_delta_EmoWell_MCMC <- stan_glm(BCovid_Dev ~ emo_well_being_delta + Covid_Exp1,
                                         family = mgcv::betar, seed = seed_no,
                                         iter= niters, weights = num_weights_3var,
                                         covid_percent %>% filter(!is.na(Covid_Exp1)))
}
df_delta_EmoWell <- covid_delta_EmoWell_MCMC %>% plot_model_IVs_stan(variable_array = c('emo_well_being_delta'), x_range = seq(-10,10,by = 0.5), return_df = TRUE) %>% as.data.frame

df_delta_EmoWell <- df_delta_EmoWell %>% mutate(
  across(!starts_with("x"),
         function(x){return(reverse_beta_squeeze(x, n=length(covid_percent %>% filter(!is.na(Covid_Exp1))),
                                                 likert_min_max = c(-4,4)))},
         .names = "{.col}_original"))

p_delta_EmoWell <- df_delta_EmoWell %>% 
ggplot(aes_string(x = "x", y = "predicted_original", group = "x_name", color = "x_name")) +
    geom_line(color = 'black') +
    geom_ribbon(aes_string(ymin = "ymin_original",
                           ymax = "ymax_original" , fill = "x_name"),fill='black', alpha = 0.3, color=NA,
                show.legend = FALSE)

p_delta_EmoWell + 
  geom_vline(xintercept = 0, linetype = 'dashed') + 
  xlab('Emotional Well-being\nImprovement in 1 Year') +
  ylab('Memory Deviation') + 
  emomem_theme + 
  theme(legend.position = 'none')

ggsave('../Output/fig/pdf/delta_wellbeing.pdf',height=6,width=6)
ggsave('../Output/fig/png/delta_wellbeing.png',height=6,width=6)

```

```{r fig3}
# Fig 3
nine11_percent <- nine11_long_avg %>% 
  #mutate(Percent = memdev / twovar_prev_experience) %>% 
  mutate(Bdev = (memdev+4)/8) %>% 
  mutate(time = relevel(factor(time), ref='2')) %>% 
  #filter(!is.na(Percent))
  filter(!is.na(Bdev)) %>% 
  filter(!is.na(prev_experience))
p_911_avg <- nine11_percent %>% 
  mutate(time = factor(time, levels = c(2:4),
                       labels = c('1 year','3 years','10 years'))) %>% 
  ggplot(aes(x=time, y=memdev)) + 
    stat_summary() + 
    stat_summary(geom='line', aes(group=1))


p_911_avg + ylab('Memory Deviation') +
  xlab('Time Interval') +
  emomem_theme

ggsave('../Output/fig/pdf/avg_911_time.pdf',height=6,width=6)
ggsave('../Output/fig/png/avg_911_time.png',height=6,width=6)

```
```{r}
sessionInfo()
```

